Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
*every* transformer has fit_transform
Also "huge difference" -> "it depends" (but it's always better).

Additionally, by leveraging the fact that \texttt{fit} always returns the
estimator it was called on, the \texttt{StandardScaler} example above can be
rewritten in a single line using method chaining:
\begin{pythoncode}
X_train = StandardScaler().fit(X_train).transform(X_train)
\end{pythoncode}
In this particular example, \texttt{fit(X\_train).transform(X\_train)} can also further
be rewritten as \texttt{fit\_transform(X\_train)}.  Combining the \texttt{fit}
and \texttt{transform} methods into a single \texttt{fit\_transform} method
indeed allows to share computations, which often makes a huge difference in practice.
In the same spirit, clustering algorithms provide a
\texttt{fit\_predict} method
that is equivalent to \texttt{fit} followed by \texttt{predict},
and thus returns the cluster labels assigned to the training data samples.

>>>>

Additionally, by leveraging the fact that \texttt{fit} always returns the
estimator it was called on, the \texttt{StandardScaler} example above can be
rewritten in a single line using method chaining:
\begin{pythoncode}
X_train = StandardScaler().fit(X_train).transform(X_train)
\end{pythoncode}

Furthermore, every estimator allows \texttt{fit(X\_train).transform(X\_train)}
to be written as \texttt{fit\_transform(X\_train)}.
The combined \texttt{fit\_transform} method prevents repeated computations.
Depending on the transformer,
this may either skip only an input validation step,
or in fact use a more efficient algorithm for the transformation.
In the same spirit, clustering algorithms provide a
\texttt{fit\_predict} method
that is equivalent to \texttt{fit} followed by \texttt{predict},
and thus returns the cluster labels assigned to the training data samples.
